Patterns of stress tolerance versus resistance in genome-wide expression data

### 2014-07-31 doc/ApTranscriptome_manuscript.Rmd
rollback changes to Intro

---
title: "Patterns of stress tolerance versus resistance in genome-wide expression data
  of parapatric ant species"
author: "John Stanton-Geddes, Andrew D. Nguyen, Mahesh Vangala, Jim Vincent, Robert R. Dunn,
  Aaron Ellison, Nate Sanders, Nicholas J. Gotelli, Sara Helms-Cahan"
csl: ecology.csl
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc_depth: 2
  html_document: null
includes: header.tex
bibliography: ApTranscriptome.bib
---

>>>>

---
title: "Patterns of stress tolerance versus resistance in genome-wide expression data
  of parapatric ant species"
author: "John Stanton-Geddes, Andrew D. Nguyen, Mahesh Vangala, Jim Vincent, Robert R. Dunn,
  Aaron Ellison, Nate Sanders, Nicholas J. Gotelli, Sara Helms-Cahan"
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc_depth: 2
  html_document: null
  word_document: default
includes: header.tex
bibliography: ApTranscriptome.bib
---
